### 2022-02-24 sections/signal_background_modeling.tex
updates and change back the version to 0.5

\subsubsection{Fake electrons and muons}
Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one $\had$. Since the fake rate of $\had$ candidate is much larger than for electron or muon, in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is prompt based on MC studies. However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, especially to $t_l\had$ where the fake-lepton dominates.
%and the jet multiplicity is low.
The contribution from these events is estimated with a data-driven method called ABCD.
The estimate is based on the number of tight and loose leptons that passed and failed the PLIV cut in the low and high $\met$ regions. The number of
fake leptons in the signal region is evaluated by rescaling the number of loose leptons in the high $\met$ region with the ratio of tight and loose leptons in the
low $\met$ region. The contribution of prompt leptons in the number of loose leptons is subtracted using MC simulation.

@@

In the leptonic channels, the events with prompt electron or muon and fake taus are modelled by calibrating MC with scale factors
derived from the dedicated $t\bar t$
control regions ($CR_{tt}$) using dileptonic decays of $t\bar t$ events and semileptonic decays of $t\bar t$ events with two
$b$-jets, summarized in Table~\ref{tab:srcr}. 	
%the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
%aimed at fake taus from different origins.
There are four kinds of fake taus that need to be calibrated: Type1) fake taus from $W$-jets ($\tau_{W}$)
with the opposite-sign (OS) of charge to the light lepton;
Type2) $\tau_{W}$'s with the same-sign (SS) charge to the light lepton; Type 3) fake taus originating from $b$-hadron decays; Type4) fake taus from light-flavour hadron decays.
The control regions are defined similar to the signal regions but with an additional $b$-jet or light lepton.
%$t_lt_l1b\thad$, $t_lt_l2b\thad$, $t_lt_h2b\thad$-2jSS, $t_lt_h2b\thad$-2jOS, $t_lt_h2b\thad$-3jSS, and $t_lt_h2b\thad$-3jOS.
The dilepton regions ($t_lt_l1b\thad$ and $t_lt_l2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The semileptonic
regions ($t_lt_h2b\thad$-2jOS and $t_lt_h2b\thad$-3jOS) where $\thad$ and light lepton have opposite charge are used to calibrate Type1 fake taus.
Similarly for the Type2, the semileptonic regions ($t_lt_h2b\thad$-2jSS and $t_lt_h2b\thad$-3jSS) where $\thad$ and light lepton have same charge are used.
A simultaneous fit to data is made to derive the scale factors for fake taus in MC, which consist of total of 24 parameters
depending on four types, three $\pt$ bins, two bins for 1- and 3-prong taus separately.
These scale factors are then used to correct the MC estimated fakes in the corresponding  signal regions with single $b$-jet.

In the $t_l\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the sameprocedure used in the $\tlhad$ channel.
%using the lepton and fake tau charges, then the scale factors are multiplied together.
The nominal value of scale factors will vary according to their uncertainties in the final fit.
%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
%control regions discussed in Section~\ref{sec:strategy_Htautau}.

>>>>

\subsubsection{Fake electrons and muons}
Electrons and muons only appear in the leptonic channels where there is exactly one electron or muon and at least one $\had$. Since the fake rate of $\had$ candidate is much larger than for electron or muon, in the majority of the fake lepton events, the $\had$ candidate is misidentified and the electron or muon is prompt based on MC studies. However the multi-jet background has large event rate and can contribute with both electron or muon and $\had$ faked, especially to $t_{\ell}\had$ where the fake-lepton dominates.
%and the jet multiplicity is low.
The contribution from these events is estimated with a data-driven method called ABCD.
The estimate is based on the number of tight and loose leptons that passed and failed the PLIV cut in the low and high $\met$ regions. The number of
fake leptons in the signal region is evaluated by rescaling the number of loose leptons in the high $\met$ region with the ratio of tight and loose leptons in the
low $\met$ region. The contribution of prompt leptons in the number of loose leptons is subtracted using MC simulation.

@@

In the leptonic channels, the events with prompt electron or muon and fake taus are modelled by calibrating MC with scale factors
derived from the dedicated $t\bar t$
control regions ($CR_{tt}$) using dileptonic decays of $t\bar t$ events and semileptonic decays of $t\bar t$ events with two
$b$-jets, summarized in Table~\ref{tab:srcr}. 	
%the SM $t\bar t$ decay of dilepton events and semileptonically double-btagged lepton-jet events, summarized in Table~\ref{tab:srcr},
%aimed at fake taus from different origins.
There are four kinds of fake taus that need to be calibrated: Type1) fake taus from $W$-jets ($\tau_{W}$)
with the opposite-sign (OS) of charge to the light lepton;
Type2) $\tau_{W}$'s with the same-sign (SS) charge to the light lepton; Type 3) fake taus originating from $b$-hadron decays; Type4) fake taus from light-flavour hadron decays.
The control regions are defined similar to the signal regions but with an additional $b$-jet or light lepton.
%$t_{\ell}t_{\ell}1b\thad$, $t_{\ell}t_{\ell}2b\thad$, $t_{\ell}t_h2b\thad$-2jSS, $t_{\ell}t_h2b\thad$-2jOS, $t_{\ell}t_h2b\thad$-3jSS, and $t_{\ell}t_h2b\thad$-3jOS.
The dilepton regions ($t_{\ell}t_{\ell}1b\thad$ and $t_{\ell}t_{\ell}2b\thad$) are used to calibrate the Type3 and Type4 fake taus. The semileptonic
regions ($t_{\ell}t_h2b\thad$-2jOS and $t_{\ell}t_h2b\thad$-3jOS) where $\thad$ and light lepton have opposite charge are used to calibrate Type1 fake taus.
Similarly for the Type2, the semileptonic regions ($t_{\ell}t_h2b\thad$-2jSS and $t_{\ell}t_h2b\thad$-3jSS) where $\thad$ and light lepton have same charge are used.
A simultaneous fit to data is made to derive the scale factors for fake taus in MC, which consist of total of 24 parameters
depending on four types, three $\pt$ bins, two bins for 1- and 3-prong taus separately.
These scale factors are then used to correct the MC estimated fakes in the corresponding  signal regions with single $b$-jet.

In the $t_{\ell}\thadhad$ channel, both taus can be misidentified, so the calibration is applied to each tau separately, following the sameprocedure used in the $\tlhad$ channel.
%using the lepton and fake tau charges, then the scale factors are multiplied together.
The nominal value of scale factors will vary according to their uncertainties in the final fit.
%In the control regions with single lepton, $\met > 20$GeV and at least 2 light jets and 2 b-tagged jets are required to ensure that QCD contribution is negligible.
%The calibration is done depending on different source of the fake taus and \pt. The calibration factor are derived in the dedicated
%control regions discussed in Section~\ref{sec:strategy_Htautau}.

### 2022-02-24 sections/systematic_uncertainties.tex

The statistical uncertainties on the fake $\had$ background calibration in the leptonic channel are applied with uncorrelated uncertainties for different fake $\had$ sources and
different $\pt$ slices. The uncertainty of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both,
its statistical fluctuation and the differences between signal regions.
The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.

>>>>

The statistical uncertainties on the fake tau background calibration in the leptonic channel are applied with uncorrelated uncertainties for different fake tau sources and
different $\pt$ slices. The uncertainty of the ABCD method is applied with a normalisation factor for muon and electron respectively considering both,
its statistical fluctuation and the differences between signal regions.
The uncertainties in the fake factor method applied in hadronic channel includes statistical uncertainties of each fake factor and different sets of fake factors derived from different signal depleted CRs.
